%
% ====================================================================================
%
%           A N S W E R S
%
% ====================================================================================
%
%
%  Answers to the questions: marked with Q in this lab description. You must include the
%  full question in your report, with your answer to the question following it.

\section{Answers}

\begin{enumerate} 
    \item \itshape What are examples of a Certificate Hierarchy graph and Web of Trust graph in use in
          the world today? Are there specific organizations that prefer one or the other?
\end{enumerate}

%==================
% Write answer here v


%=================

\begin{enumerate}[resume]
    \item \itshape How does the .p12 file work? Explain what this file is and its relationship to the 
          \textnormal{NTNU CA}
\end{enumerate}

%==================
% Write answer here v


%=================

\begin{enumerate}[resume]
    \item \itshape Comment on security related issues regarding the cryptographic algorithms used to
          generate and sign your group’s web server certificate (key lengths, algorithms, etc.).
\end{enumerate}

%==================
% Write answer here v


%=================

\begin{enumerate}[resume]
    \item \itshape List and explain each of the verifications. What is the difference between the two files?
Who has signed the Apache release? What is the point of this process?
\end{enumerate}

%==================
% Write answer here v


%=================

\begin{enumerate}
    \item \itshape  What is the purpose of a certificate chain? Describe, on a high-level, the steps that your
          browser takes when verifying the authenticity of a web page served over \textnormal{HTTPS}.
\end{enumerate}

%==================
% Write answer here v


%=================

\begin{enumerate}[resume]
    \item \itshape Web servers offering weak cryptography are subject to several attacks. List 3 specific
          feasible attacks that are possible due to weak cryptography and explain them briefly. How
          did you configure your server to prevent such attacks? (Note that answers describing attacks
          which are possible due to other weaknesses, or describing general categories of attacks will not
          receive credit.)
\end{enumerate}

%==================
% Write answer here v


%=================